% ------------ Title Page

\begin{titlepage}
    \centering
    \vspace*{1in}

    \Huge
    \textbf{Title of the Document}

    \vspace{0.5in}

    \LARGE
    Subtitle or Description

    \vspace{1.5in}

    \textbf{Author Name}

    \vfill

    A Thesis Submitted for the Degree of\\ Doctor of Philosophy\\ in the Department
    of Example\\ University Name

    \vspace{0.8in}

    \textbf{Month Year}

\end{titlepage}

% ------------ Headers and Footers

\documentclass{article}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields

% Header
\fancyhead[L]{Left Header} % Left side of header
\fancyhead[C]{Center Header} % Center of header
\fancyhead[R]{Right Header} % Right side of header

% Footer
\fancyfoot[L]{Left Footer} % Left side of footer
\fancyfoot[C]{\thepage} % Center of footer with page number
\fancyfoot[R]{Right Footer} % Right side of footer

% ------------- Page numbers

\begin{document}

% Page number settings
\pagenumbering{arabic} % Use Arabic numerals (1, 2, 3, ...)
% \pagenumbering{roman} % Use Roman numerals (i, ii, iii, ...)
% \pagenumbering{Roman} % Use uppercase Roman numerals (I, II, III, ...)
% \pagenumbering{alph} % Use lowercase letters (a, b, c, ...)
% \pagenumbering{Alph} % Use uppercase letters (A, B, C, ...)

\section{Introduction}
This document demonstrates different page number styles.
\end{document}

% ------------- restart page numbering

\documentclass{article}

\begin{document}

% Title Page
\begin{titlepage}
...
\end{titlepage}

\newpage
\pagenumbering{arabic} % Restart page numbering from this point
\setcounter{page}{1}

\section{Introduction}
This page starts with page number 1.

\newpage
\section{Next Section}
Continues page numbering from previous section.

\end{document}

% -------------- Page Layout 

\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}

\begin{document}

\section{Introduction}
This document uses custom page margins.

\end{document}

% ------------- create appendix-table of content

% ---- basic appendix

\documentclass{article}
\usepackage{appendix} % For appendix functionality

\begin{document}

\tableofcontents % Table of contents
\newpage

\section{Introduction}
This is the introduction section.

\section{Main Content}
This is the main content section.

% Adding appendices
\newpage
\begin{appendices}
\section{First Appendix}
This is the first appendix.

\section{Second Appendix}
This is the second appendix.
\end{appendices}

\end{document}

% --------------- use tocobibind - appendix add to table of content

\documentclass{report}
\usepackage{tocbibind} % Automatically include appendix in the table of contents

\begin{document}

\tableofcontents % Table of contents
\newpage

\chapter{Introduction}
This is the introduction chapter.

\chapter{Main Content}
This is the main content chapter.

% Adding appendices
\appendix
\chapter{First Appendix}
\section{Details of the First Appendix}
Detailed content for the first appendix.

\chapter{Second Appendix}
\section{Details of the Second Appendix}
Detailed content for the second appendix.

\end{document}

